\paragraph{Notation.}
\label{sec:prelims}
\input{prelims}

\subsubsection*{The algorithm}


%%%%%%%%%%%%%%%% alg-custom-block %%%%%%%%%%%%
\algblock{ArmElim}{EndArmElim}
\algnewcommand\algorithmicArmElim{\textbf{\em Arm Elimination}}
 \algnewcommand\algorithmicendArmElim{}
\algrenewtext{ArmElim}[1]{\algorithmicArmElim\ #1}
\algrenewtext{EndArmElim}{\algorithmicendArmElim}

\algblock{ClusElim}{EndClusElim}
\algnewcommand\algorithmicClusElim{\textbf{\em Cluster Elimination}}
 \algnewcommand\algorithmicendClusElim{}
\algrenewtext{ClusElim}[1]{\algorithmicClusElim\ #1}
\algrenewtext{EndClusElim}{\algorithmicendClusElim}
\algtext*{EndArmElim}
\algtext*{EndClusElim}

\algblock{ResParam}{EndResParam}
\algnewcommand\algorithmicResParam{\textbf{\em Reset Parameters}}
 \algnewcommand\algorithmicendResParam{}
\algrenewtext{ResParam}[1]{\algorithmicResParam\ #1}
\algrenewtext{EndResParam}{\algorithmicendResParam}

\begin{algorithm}[t]
\caption{ClusUCB}
\label{alg:clusucb}
\begin{algorithmic}
\State {\bf Input:} Number of clusters $p$, time horizon $T$, exploration parameters $\rho_a$, $\rho_s$ and $\psi$.
\State {\bf Initialization:} Set $B_{0}:=A$, $S_0 = S$ and $\epsilon_{0}:=1$.
\State Create a partition $S_0$ of the arms at random into $p$ clusters of size up to $\ell=\bigg\lceil \dfrac{K}{p} \bigg\rceil$ each.
\For{$m=0,1,..\big \lfloor \dfrac{1}{2}\log_{2} \dfrac{T}{e}\big\rfloor$}	
\State Pull each arm in $B_m$ so that the total number of times it has been pulled is $n_{m}=\bigg\lceil\dfrac{\log{(\psi T\epsilon_{m}^{2})}}{2\epsilon_{m}}\bigg\rceil$. 
% A partition of $A$ into clusters from Algorithm \ref{alg:rua}
%\State \hspace*{2em} Calculate $w_{s_{i}}=\bigg\lceil\dfrac{1}{\ell\hat{\Delta}_{s_{i}}}\bigg\rceil$,if $\hat{\Delta}_{s_{i}}\neq 0, \forall s_{i}\in S$
%\newline\hspace*{8em}$=1$, otherwise, and $\hat{\Delta}_{s_{i}}=\max_{i\in s_{i}}{\lbrace\hat{r}_{i}\rbrace}-\min_{j\in s_{i}}{\lbrace\hat{r}_{j}\rbrace}, i\neq j$
\ArmElim
\State For each cluster $s_k \in S_{m}$, delete arm ${i}\in s_{k}$ from $B_{m}$ if
\begin{align*}
\hat{r}_{i} + \sqrt{\dfrac{\rho_{a}\log{(\psi T\epsilon_{m})}}{2 n_{m}}}  < \max_{{j}\in s_{k}}\bigg\lbrace\hat{r}_{j} -\sqrt{\dfrac{\rho_{a}\log{(\psi T\epsilon_{m})}}{2 n_{m}}} \bigg\rbrace
\end{align*}
% where $\rho_{a}=\dfrac{1}{w_{m}}$ and remove all such arms from $B_{m}$.
\EndArmElim
\ClusElim
\State Delete cluster $s_{k}\in S_{m}$ and remove all arms $i\in s_{k}$ from $B_{m}$ if 
\begin{align*}
 \max_{{i}\in s_{k}}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{\rho_{s}\log{(\psi T\epsilon_{m})}}{2 n_{m}}}\bigg\rbrace  
 < \max_{{j}\in B_{m}} \bigg\lbrace\hat{r}_{j} - \sqrt{\dfrac{\rho_{s} \log{(\psi T\epsilon_{m})}}{2 n_{m}}}\bigg\rbrace.
\end{align*}
%  and remove all such arms in the cluster $s_{k}$ from $B_{m}$ to obtain $B_{m+1}$.
\EndClusElim
\State Set $\epsilon_{m+1}:=\dfrac{\epsilon_{m}}{2}$\vspace{0.5ex}
\State Set $B_{m+1}:=B_{m}$
\State Stop if $|B_{m}|=1$ and pull ${i}\in B_{m}$ till $T$ is reached.
\EndFor
\end{algorithmic}
\end{algorithm}

%\todos[inline]{Shouldn't there be a $\psi$ inside the log term on RHS of both elim conditions of Algorithm \ref{alg:clusucb}? (Subho) Addressed: $\psi$ has to be there}

As mentioned in a recent work \cite{liu2016modification}, UCB-Improved has two shortcomings: 	\\
\begin{inparaenum}[\bfseries(i)]
\item A significant number of pulls are spent in early exploration, since each round $m$ of UCB-Improved involves pulling every arm an identical $n_{m}=\bigg\lceil \dfrac{ 2\log(T\epsilon^{2}_{m})}{\epsilon^{2}_{m}} \bigg\rceil$ number of times. The quantity $\epsilon_{m}$ is initialized to $1$ and halved after every round.\\
\item In UCB-Improved, arms are eliminated conservatively, i.e, only after $\epsilon_{m}<\dfrac{\Delta_{i}}{2}$, the sub-optimal arm $i$ is discarded with high probability. This is disadvantageous when $K$ is large and the gaps are identical ($r_{1}=r_{2}=..=r_{K-1}<r^{*}$) and small.\\
\end{inparaenum}
To reduce early exploration, the number $n_m$ of times each arm is pulled per round in ClusUCB is lower than that of UCB-Improved and also that of Median-Elimination, which used $n_m=\dfrac{4}{\epsilon^{2}}\log\big(\dfrac{3}{\delta}\big)$, where $\epsilon,\delta$ are confidence parameters.
To handle the second problem mentioned above, ClusUCB partitions the larger problem into several small sub-problems using clustering and then performs local exploration aggressively to eliminate sub-optimal arms within each clusters with high probability.


As described in the pseudocode in Algorithm~\ref{alg:clusucb}, ClusUCB begins with a initial clustering of arms that is performed by random uniform allocation. The set of clusters $S$ thus obtained satisfies $|S|=p$, with individual clusters having a size that is bounded above by $\ell=\bigg\lceil \dfrac{K}{p} \bigg\rceil$.
Each round of ClusUCB involves both individual arm as well as cluster elimination conditions. These elimination conditions are inspired by UCB-Improved. Notice that, unlike UCB-Improved, there is no longer a single point of reference based on which we are eliminating arms. Instead now we have as many reference points to eliminate arms as number of clusters formed. 
%Further, the exploration factors $\rho_{a}\in (0,1]$ and $\rho_{s}\in (0,1]$ governing the arm and cluster elimination conditions, respectively, are relatively more aggressive than that in UCB-Improved. 

The exploration regulatory factor $\psi$ governing the arm and cluster elimination conditions in ClusUCB is more aggressive than that in UCB-Improved. With appropriate choice of $\psi$ and $\rho_a$ and $\rho_s$ we can achieve aggressive elimination even when the gaps $\Delta_i$ are small and $K$ is large. 

%and the gaps $\Delta_i$ are small, it is efficient to remove sub-optimal arms quickly. 

In \cite{liu2016modification}, the authors recommend incorporating a factor of $d_i$ inside the log-term of the UCB values, i.e., $\max \lbrace\hat{r}_{i}+\sqrt{\frac{d_{i}\log T{\epsilon}_{m}^{2}}{2n_{m}}}\rbrace$. 
The authors there examine the following choices for $d_i$: $\frac{T}{t_{i}}$, $\frac{\sqrt{T}}{t_{i}}$ and $\frac{\log T}{t_{i}}$, where $t_{i}$ is the number of times an arm ${i}$ has been sampled.
Unlike \cite{liu2016modification}, we employ cluster as well as arm elimination and establish from a theoretical analysis that the choice $\psi=\frac{T}{\log (KT)}$ helps in achieving a better gap-dependent regret upper bound for ClusUCB as compared to UCB-Improved and MOSS (see Corollary \ref{Result:Corollary:1} in the next section). 




